A Practical Optional Type System for Clojure

### 2012-11-24 dissertation/intro.tex
Correct typos in dissertation
Fix defn -> def explanation

(\lstinline|(defn [...] body)| expands to \lstinline|(def (fn [...] body))|
where \lstinline|def| defines a new var and \lstinline|fn| creates a function value).

@@

Listing \ref{lst:singletoneeg} shows a simple example of using
singleton types in Typed Clojure.
Singleton types are are discussed further in section \ref{sec:intersectionunion}.

>>>>

(\lstinline|(defn name [...] body)| expands to \lstinline|(def name (fn [...] body))|,
where \lstinline|(def name init)| defines a new var in the current namespace 
called \lstinline|name|, and \lstinline|fn| creates a function value).

@@

Listing \ref{lst:singletoneeg} shows a simple example of using
singleton types in Typed Clojure.
Singleton types are discussed further in section \ref{sec:intersectionunion}.
